Limits to Ecological Forecasting: Estimating Uncertainty for Critical Transitions with Deep Learning

### 2022-09-20 manuscript/manuscript.Rmd
Fixing some captions

```{r figure3, fig.height=7}
#| fig.cap="Forecasts of the Hopf bifurcation under each model, compared to 15 realizations of the true model. 
#|  The bifurcation occurs soon after forecasting period begins, 
#| leading to progressively larger and larger oscillations. 
#|  Prior to the bifurcation, pseudo-cycles are visible in the training data due to stochastic excitations. 
#|  Following the bifurcation, stochasticity blurs the oscillatory pattern across replicate simulations. 
#|  Only last 25 time points of training data are shown."

@@

```{r figure6}
#| fig.cap="CRPS scores over time for each scenario.
#|  Each line represents the CRPS scores against a replicate of time series observations from the 'true model'. 
#|  The general pattern across these plots is that forecast skill gets worse over time -- gradually 
#|  in the case of a Hopf bifurcation or suddenly in response to the saddle-node bifurcation. 
#|  In the stochastic transition case,  the scores tend to diverge in two branches, where high values indicate periods of 
#|  time when the forecast predicts the wrong equilibrium state and the lower branch indicates predicting the correct one."

>>>>

```{r figure3, fig.height=7}
#| fig.cap="Forecasts of the Hopf bifurcation under each model, compared to 15 realizations of the true model. 
#|  The bifurcation occurs soon after the forecasting period begins, 
#|  leading to progressively larger oscillations. 
#|  Prior to the bifurcation, pseudo-cycles are visible in the training data due to stochastic excitations. 
#|  Following the bifurcation, stochasticity blurs the oscillatory pattern across replicate simulations. 
#|  Only the last 25 time points of the training data are shown."

@@

```{r figure6}
#| fig.cap="CRPS scores over time for each scenario.
#|  Each line represents the CRPS scores against a replicate of time series observations from the 'true model'. 
#|  The general pattern across these plots is that forecast skill gets worse over time -- gradually 
#|  in the case of a Hopf bifurcation or suddenly in response to the saddle-node bifurcation. 
#|  In the stochastic transition case,  the scores tend to diverge in two branches, where high values indicate periods of 
#|  time when the forecast predicts the wrong equilibrium state and the lower branch indicates predictions of the correct one. The time axis in this plot and in Figure 7 refers to the time from the beginning of the forecast window, not the time from the beginning of the time series as in other plots."
